Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-04-26 ms/LMA_method.Rmd

---
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
#font-famliy: "ebgaramond"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
  - \linenumbers
output:
  html_document:
    toc: FALSE
  pdf_document:
    keep_md: false
    fig_caption: yes
    keep_tex: yes
    toc: no
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    pandoc_arg:
      - "--filter"
      - "pandoc-crossref"
  bookdown::word_document2:
    fig_width: 6
    fig_caption: yes
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

@@

*Statistical analyses*

*new subsection*

To quantify the effect of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA, we built hierarchical Bayes models.
The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of  leaf size and leaf thickness on the log-scale;

$$
\mathrm{ln}(LMA_{Wi}) \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i)
$$

$$
\tilde{\mu_i} = \beta_0 + \beta_1 \mathrm{ln}(LA_{i}) + \beta_2 \mathrm{ln}(LT_{i})
$$

@@

$$
\mathrm{ln}(\sigma_i) \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega)
$$

$$
\tilde{\sigma_i} = \gamma_0 + \gamma_1 \mathrm{ln}(LA_{i}) + \gamma_2 \mathrm{ln}(LT_{i})
$$

@@

*new subsection*

@@

*new subsection?*

@@

$$
CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N}
$$

>>>>

---
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
#font-famliy: "ebgaramond"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
  - \linenumbers
output:
  html_document:
    toc: FALSE
#  pdf_document:
  bookdown::pdf_document2:
    keep_md: false
    fig_caption: yes
    keep_tex: yes
    toc: no
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    pandoc_arg:
      - "--filter"
      - "pandoc-crossref"
  bookdown::word_document2:
    fig_width: 6
    fig_caption: yes
    number_sections: no
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

@@

*Effects of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA*

To quantify the effect of leaf area and thickness on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of  leaf area and leaf thickness on the log-scale;

\begin{align}
\mathrm{ln}(LMA_{Wi}) & \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i) (\#eq:LMA)\\
\tilde{\mu_i} & = \beta_0 + \beta_1 \mathrm{ln}(LA_{i}) + \beta_2 \mathrm{ln}(LT_{i}) (\#eq:mu)
\end{align}

@@

\begin{align}
\mathrm{ln}(\sigma_i) & \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega) (\#eq:ln-sigma) \\
\tilde{\sigma_i} & = \gamma_0 + \gamma_1 \mathrm{ln}(LA_{i}) + \gamma_2 \mathrm{ln}(LT_{i}) (\#eq:tilde-sigma)
\end{align}

@@

*Bivariate trait relationships for mean and CV*

@@

@@

\begin{align}
CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N} (\#eq:CV)
\end{align}

### 2022-04-26 ms/LMA_method.tex

\emph{Statistical analyses}

\emph{new subsection}

@@

\[
\mathrm{ln}(LMA_{Wi}) \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i)
\]

\[
\tilde{\mu_i} = \beta_0 + \beta_1 \mathrm{ln}(LA_{i}) + \beta_2 \mathrm{ln}(LT_{i})
\]

@@

\[
\mathrm{ln}(\sigma_i) \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega)
\]

\[
\tilde{\sigma_i} = \gamma_0 + \gamma_1 \mathrm{ln}(LA_{i}) + \gamma_2 \mathrm{ln}(LT_{i})
\]

@@

\emph{new subsection}

@@

\emph{new subsection?}

@@

\[
CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N}
\]

>>>>

\emph{Effects of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA}

@@

\begin{align}
\mathrm{ln}(LMA_{Wi}) & \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i) \label{eq:LMA}\\
\tilde{\mu_i} & = \beta_0 + \beta_1 \mathrm{ln}(LA_{i}) + \beta_2 \mathrm{ln}(LT_{i}) \label{eq:mu}
\end{align}

@@

\begin{align}
\mathrm{ln}(\sigma_i) & \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega) \label{eq:ln-sigma} \\
\tilde{\sigma_i} & = \gamma_0 + \gamma_1 \mathrm{ln}(LA_{i}) + \gamma_2 \mathrm{ln}(LT_{i}) \label{eq:tilde-sigma}
\end{align}

@@

\emph{Bivariate trait relationships}

@@

\emph{Intraspecifc variation}

@@

\begin{align}
CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N} \label{eq:CV}
\end{align}
